\begin{thebibliography}{1}
	

\bibitem{lit-review:tennis}
	Brookheaven~National~Laboratory,~"The First Video Game?",~Brookheaven~National~Laboratory, 1958. [Online] Available: https://www.bnl.gov/about/history/firstvideo.php

\bibitem{lit-review:definition}
	Oxford Dictionaries,~" Video Game", 2017. [Online] Available: "https://en.oxforddictionaries.com/definition/video\_game"


\bibitem{lit-review:darmouth}
	John McCarthy, Marvin L. Minsky, Nathaniel Rochester,and Claude E. Shannon,~"A Proposal for the Dartmouth Summer Research Project on Artificial Intelligence", August 31, 1955.

\bibitem{lit-review:darmouth}
	Emma McDonald,~"The Global Games Market Will Reach \$108.9 Billion in 2017 With Mobile Taking 42", Aprl 20, 2017. [Online] Available: https://newzoo.com/insights/articles/the-global-games-market-will-reach-108-9-billion-in-2017-with-mobile-taking-42/

\bibitem{lit-review:dijkstra}
	Dijkstra, E. W. (1959). "A note on two problems in connexion with graphs". Numerische Mathematik. 1: 269–271. doi:10.1007/BF01386390.

\bibitem{lit-review:khatib}
 O. Kathib. "Real-time obstacle avoidance for manipulators and mobile robots". The international Journal of Robotics Research, Vol 5, no.1,pp. 90-98, 1986.


\bibitem{lit-review:car}
 Johan Hagelbäck and Stefan J. Johansson, “A Multiagent Potential Field-Based Bot for Real-Time Strategy Games,” International Journal of Computer Games Technology, vol. 2009, Article ID 910819, 10 pages, 2009. 
  
\bibitem{lit-review:intelligent}
F. Dignum, J. Westra, W. A. van Doesburg, and M. Harbers, "Games and Agents: Designing Intelligent Gameplay" International Journal of Computer Games Technology, vol. 2009, Article ID 837095, 18 pages, 2009.


\bibitem{lit-review:HMM}
Cedric Beaulac and Fabrice Larribe, "Narrow Artificial Intelligence with Machine Learning for Real-Time Estimation of a Mobile Agent’s Location Using Hidden Markov Models" International Journal of Computer Games Technology, vol. 2017, Article ID 4939261, 10 pages, 2017. 


\bibitem{lit-review:unify}
Firas Safadi, Raphael Fonteneau, and Damien Ernst, "Artificial Intelligence in Video Games: Towards a Unified Framework" International Journal of Computer Games Technology, vol. 2015, Article ID 271296, 30 pages, 2015.


\bibitem{lit-review:unify}
Zeyad Abd Algfoor, Mohd Shahrizal Sunar, and Hoshang Kolivand, "A Comprehensive Study on Pathfinding Techniques for Robotics and Video Games" International Journal of Computer Games Technology, vol. 2015, Article ID 736138, 11 pages, 2015.


\end{thebibliography}